\pkg{systemfit}: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-12-27 paper/trunk/systemfit.tex
using now (hopefully) always \proglang, \pkg, and \code (also in titles, references, ...)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@908 591db2bd-e0a0-4d22-8c19-2192dbb7da31
changed \Shorttitle: "systemfit" -> "\pkg{systemfit}: A Package for Estimating Systems of Simultaneous Equations in \proglang{R}"
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@909 591db2bd-e0a0-4d22-8c19-2192dbb7da31

\title{systemfit: A Package for Estimating\\
       Systems of Simultaneous Equations in \proglang{R}}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Arne Henningsen, Jeff D.\ Hamann} %% comma-separated
\Plaintitle{systemfit: A Package for Estimating Systems of Simultaneous Equations
            in R} %% without formatting
\Shorttitle{systemfit} %% a short title (if necessary)

>>>>

\title{\pkg{systemfit}: A Package for Estimating\\
       Systems of Simultaneous Equations in \proglang{R}}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Arne Henningsen, Jeff D.\ Hamann} %% comma-separated
\Plaintitle{systemfit: A Package for Estimating Systems of Simultaneous Equations
            in R} %% without formatting
\Shorttitle{\pkg{systemfit}: A Package for Estimating
   Systems of Simultaneous Equations in \proglang{R}}
   %% a short title (if necessary)
